Elicitation Complexity via Convex Piecewise Linear Loss Functions

### 2018-11-12 fplc-elic.tex
meeting notes
Fixed \Gamma' to \gamma updates and added questions I had

\begin{proposition}
  If elicitable $\Gamma:\P\toto\reals^d$ embeds non-degenerate $\gamma:\P\toto\R$, there is a selective link $f:\reals^d\to\R$ from $\Gamma$ to $\gamma$.
\end{proposition}
\begin{proof}
  Let $\V = \bigcap\{ \Gamma(p) : p\in\P\} \subseteq \reals^d$ be the image of $\Gamma$.
  Define $F:\V\toto\R$ as follows: $F(v) = \bigcap\{\gamma(p) : v\in\Gamma(p)\} = \bigcap\{\gamma(p) : p \in\Gamma_v\}$.
  That is, $F$ encodes all reports of $\gamma$ which could be correct when $v$ is chosen from $\Gamma$.
  Now let $v\in\V$, and let $r\in\R$ be given by Lemma~\ref{lem:embed-lev-set-subset}, so that $\Gamma_v \subseteq \gamma_r$.
  Then $p\in\Gamma_v \implies r\in\gamma(p)$, so we have $r \in F(v)$, and in particular, $F(v)\neq\emptyset$.
  (The latter would be vacuous if there were no $p\in\Gamma_v$, but we have assumed so by definition of $\V$.)
  We simply define $f:\reals^d$ to be any single-valued function such that $f(\varphi(r)) = r$ for all $r\in\R$, $f(v) \in F(v)$ whenever $v\in\V$, and $f(v) \in \R$ arbitrary when $v\notin\V$.
  (This is a consistent choice by definition of $\varphi$.)

  It remains to show that $f$ is a selective link.
  For (i), note that $r'\in\Gamma'(p) \implies F(r') \subseteq \Gamma(p) \implies f(r') \in \Gamma(p)$.
  For (ii), let $p$ be given.
  For all $r\in\Gamma(p)$, we must have $\varphi(r) \in \Gamma'(p)$ by definition of $\varphi$.
  Thus, $f(\Gamma'(p)) \supseteq \{f(\varphi(r)) : r \in \Gamma(p)\} = \Gamma(p)$.
  By (i), this must be an equality.
\end{proof}

\begin{proposition}
  Let $\Gamma:\P\toto\reals^d$ be elicitable.
  The following are equivalent:
  \begin{enumerate}
  \item $\Gamma$ is an embedding of a finite elicitable property.
  \item $\Gamma$ has finitely many full-dimensional level sets which union to $\P$.
  \item $\Gamma$ has finitely many full-dimensional level sets which union to $\P$, and a report in each level set such that...
  \item $\strip(\Gamma)$ is finite.
  \item $\trim(\Gamma)$ is finite.
  \item $\trim(\Gamma)$ is finite and elicitable.
  \end{enumerate}
\end{proposition}
\begin{proof}
  \raf{Much of the proof in Jessie-notes}
\end{proof}

@@

\raf{Do we also have $d$-embeddable $\implies$ $d$-FPLC-embeddable if $\gamma$ is finite?  That seems harder to show; maybe it was on our list once.}

@@

Implications for complexity: certainly $\gamma$ is $d$-FPLC-embeddable $\implies$ $\elic_\FPLC(\gamma) \leq d$.
\raf{If $\gamma$ is elicitable, I think this is an $\iff$, right?}
If $\gamma$ is finite but not elicitable, it will not be FPLC-embeddable for any dimension, but could still have finite FPLC elicitation complexity.
E.g.\

>>>>

\begin{proposition}
  If elicitable $\Gamma:\P\toto\reals^d$ embeds non-degenerate $\gamma:\P\toto\R$, there is a selective link $f:\reals^d\to\R$ from $\Gamma$ to $\gamma$.
\end{proposition}
\begin{proof}
  Let $\V = \bigcap\{ \Gamma(p) : p\in\P\} \subseteq \reals^d$ be the image of $\Gamma$.
  Define $F:\V\toto\R$ as follows: $F(v) = \bigcap\{\gamma(p) : v\in\Gamma(p)\} = \bigcap\{\gamma(p) : p \in\Gamma_v\}$.
  That is, $F$ encodes all reports of $\gamma$ which could be correct when $v$ is chosen from $\Gamma$.
  Now let $v\in\V$, and let $r\in\R$ be given by Lemma~\ref{lem:embed-lev-set-subset}, so that $\Gamma_v \subseteq \gamma_r$.
  Then $p\in\Gamma_v \implies r\in\gamma(p)$, so we have $r \in F(v)$, and in particular, $F(v)\neq\emptyset$.
  (The latter would be vacuous if there were no $p\in\Gamma_v$, but we have assumed so by definition of $\V$.)
  We simply define $f:\reals^d \to \R$ to be any single-valued function such that $f(\varphi(r)) = r$ for all $r\in\R$, $f(v) \in F(v)$ whenever $v\in\V$, and $f(v) \in \R$ arbitrary when $v\notin\V$.
  (This is a consistent choice by definition of $\varphi$.)

  It remains to show that $f$ is a selective link.
  For (i), note that $r'\in\Gamma'(p) \implies F(r') \subseteq \Gamma(p) \implies f(r') \in \Gamma(p)$.
  For (ii), let $p$ be given.
  For all $r\in\Gamma(p)$, we must have $\varphi(r) \in \gamma(p)$ by definition of $\varphi$ \jessiet{Doesn't matter too much, but notation doesn't match Definition 3}.
  Thus, $f(\gamma(p)) \supseteq \{f(\varphi(r)) : r \in \Gamma(p)\} = \Gamma(p)$.
  By (i), this must be an equality.
\end{proof}

\begin{proposition}
  Let $\Gamma:\P\toto\reals^d$ be elicitable.
  The following are equivalent:
  \begin{enumerate}
  \item $\Gamma$ is an embedding of a finite elicitable property.
  \item $\Gamma$ has finitely many full-dimensional level sets which union to $\P$.
  \item \rotatebox{180}{$\Gamma$ has finitely many full-dimensional level sets which union to $\P$.}
  \item $\strip(\Gamma)$ is finite.
  \item $\trim(\Gamma)$ is finite.
  \item $\trim(\Gamma)$ is finite and elicitable.
  \end{enumerate}
\end{proposition}
\begin{proof}
  \raf{Much of the proof in Jessie-notes}
\end{proof}

@@

\raf{Do we also have $d$-embeddable $\implies$ $d$-FPLC-embeddable if $\gamma$ is finite?  That seems harder to show; maybe it was on our list once.}\jessie{Not as hard to show if embeddable $\iff$ FPLC}

@@

Implications for complexity: certainly $\gamma$ is $d$-FPLC-embeddable $\implies$ $\elic_\FPLC(\gamma) \leq d$.
\raf{If $\gamma$ is elicitable, I think this is an $\iff$, right?}
If $\gamma$ is finite but not elicitable, it will not be FPLC-embeddable for any dimension, but could still have finite FPLC elicitation complexity.
E.g.\ 
\jessie{Example?  This statement's a little surprising to me since the FPLC $L$ would elicit some other property $\Gamma$ and $\gamma$ would also embed some finite elicitable property $\zeta$... but if $\strip(\gamma) \neq \strip(\zeta) = \trim(\Gamma)$ then how does $\Gamma$ embed $\gamma$?  Maybe I'm too fixed on FPLCs...}
